Another Look at Regularized Discriminant Analysis for High-Dimensional Classification

### 2013-04-21 reports/paper-rda.Rnw
Updated figures to abide by Biometrika rules.

# To abide by Biometrika's requirements of no abbreviations, we rename the
# results of our HDRDA classifier as simply "Ours."
results$Ours <- results$HDRDA
results <- subset(results, select = -HDRDA)

@@

# Summary of the classification error rates for each data set and number of
# variables selected, d.
error_rates <- subset(results, select = -c(lambda, gamma))
m_error <- melt(error_rates, variable.name = "Classifier", value.name = "Error")
m_error$Classifier <- factor(m_error$Classifier)
error_rates <- ddply(m_error, .(data_set, d, Classifier), plyr:::summarize,
                     Avg_Error = mean(Error), Num_Reps = length(Error))
error_rates <- ddply(error_rates, .(data_set, d, Classifier), transform,
                     SE_Error = sqrt(Avg_Error * (1 - Avg_Error) / Num_Reps))
error_rates <- subset(error_rates, select = -Num_Reps)

# Candidate values of tuning parameters.
seq_lambda <- seq(0, 1, by = 0.05)
seq_gamma <- 10^seq.int(-1, 5)

# Summary of the optimal tuning-parameter estimates for each data set and number
# of variables selected, d.
hdrda_optimal <- subset(results, select = c(data_set, d, lambda, gamma))
hdrda_optimal$lambda <- factor(hdrda_optimal$lambda, levels = seq_lambda)
hdrda_optimal$gamma <- factor(hdrda_optimal$gamma, levels = seq_gamma)

hdrda_optimal <- ddply(hdrda_optimal, .(data_set, d), function(x) {
  x <- subset(x, select = c(lambda, gamma))
  melt(table(x))
})

@@

\begin{figure}
<<error_rates>>=
error_rates$data_set <- Hmisc:::capitalize(error_rates$data_set)
p <- ggplot(error_rates, aes(x = d, y = Avg_Error, group = Classifier))
p <- p + geom_line(aes(color = Classifier, linetype = Classifier), size = 1.5)
p <- p + facet_wrap(~ data_set) + ylim(c(0, max(error_rates$Avg_Error))) + theme_bw()
p <- p + xlab("Number of Variables Selected") + ylab("Average Error Rate")
p  + theme(strip.text.x = element_text(size = 12))
@ 
\caption{Average error-rate estimates of the competing classifiers as a function
  of $d$. Approximate standard errors are no greater than \Sexpr{max(error_rates[["SE_Error"]])}.}
\label{fig:error-rates}
\end{figure}

>>>>

@@

# Summary of the classification error rates for each data set and number of
# variables selected, d.
error_rates <- subset(results, select = -c(lambda, gamma))
m_error <- melt(error_rates, variable.name = "Classifier", value.name = "Error")
error_rates <- ddply(m_error, .(data_set, d, Classifier), plyr:::summarize,
                     Avg_Error = mean(Error), Num_Reps = length(Error))
error_rates <- ddply(error_rates, .(data_set, d, Classifier), transform,
                     SE_Error = sqrt(Avg_Error * (1 - Avg_Error) / Num_Reps))
error_rates <- subset(error_rates, select = -Num_Reps)
@

@@

\begin{figure}
<<error_rates>>=
error_rates$data_set <- Hmisc:::capitalize(error_rates$data_set)
p <- ggplot(error_rates, aes(x = d, y = Avg_Error, group = Classifier))
p <- p + geom_line(aes(color = Classifier), size = 1.5, linetype = 2)
p <- p + geom_point(aes(color = Classifier, shape = Classifier), size = 4)
p <- p + facet_wrap(~ data_set) + ylim(c(0, max(error_rates$Avg_Error))) + theme_bw()
p <- p + xlab("Number of Variables Selected, d") + ylab("Average Error Rate")
p <- p + theme(axis.text = element_text(size = 16))
p <- p + theme(axis.title.x = element_text(size = 20))
p <- p + theme(axis.title.y = element_text(size = 20))
p <- p + theme(strip.text.x = element_text(size = 18))
p + theme(legend.position = "none")
@ 
\caption{Averages of the 1000 error-rate estimates of the competing classifiers
  for each data set as a function of $d$. The classifiers are marked as follows:
  Dudoit (red circle), Guo (gold triangle), Pang (green square), Tong = (cyan
  cross), Witten (blue square with X), and ours (pink asterisk). Approximate
  standard errors are no greater than \Sexpr{max(error_rates[["SE_Error"]])}.}
\label{fig:error-rates}
\end{figure}
